Sound and Automated Synthesis of Digital Controllers for Physical Plants

### 2016-10-08 paper/paper.tex
review Synthesis elements specific to control systems

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\red{Automated} Program Synthesis for \red{for Controllers}}

@@

\paragraph{Synthesis elements specific to control systems}
Next, we describe the specific property that we pass to the 
program synthesiser as the specification $\sigma$.
There are two different algorithms in DSVerifier that can be used for
stability verification, one based on Schur's decomposition and another
one based on Jury's criteria \cite{DBLP:journals/dafes/BessaICF16} \red{[Jury here is our friend, I wouldn't use his first name ... ]}.
Here, we choose Jury's method, due to its efficiency.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Automated Program Synthesis \\ for Digital Controllers}

@@

\paragraph{Synthesis elements specific to control systems}
Next, we describe the specific property that we pass to the 
program synthesiser as the specification $\sigma$.
There are two different algorithms in DSVerifier that can be used for
stability verification~\cite{DBLP:journals/dafes/BessaICF16}, 
one based on Schur's decomposition and another one based on 
Jury's criteria~\cite{astrom1997computer}.
Here, we choose Jury's method~\cite{astrom1997computer}, due to its efficiency.
